\documentclass{beamer}
\usetheme{Boadilla}
\usepackage{cite}

% Look at other themes?

\title{Architecting Effective Map Streaming in Low-Bandwidth Scenarios}
\subtitle{An inspiring and amazing research question that everyone wants to know, but was too afraid to write a 2000-word essay about.}
\author{Louis Foy}
\institute{Falmouth University}
\date{\today}

\begin{document}
\begin{frame}
	\titlepage
\end{frame}

\section{The Question}
\begin{frame}
	\frametitle{The Question}
	\begin{itemize}
		\item Which C++ architecture(s) could best support QoE-oriented map streaming in a player-building-based multiplayer game?
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{A scenario}
	\begin{itemize}
		\item My company wants to make a large-scale, multiplayer building game
		\item Players can build complex structures in real-time
		\item It\textquoteright s releasing across the world
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{A problem}
	\begin{itemize}
		\item Map data downloads take a lot of bandwidth
		\item Large markets, such as Egypt, Brazil, and China, suffer from slow broadband 
		\begin{itemize}
			\item Even though China is the world’s strongest gaming market! \cite{chinamarket}
		\end{itemize}
		\item This risks leaving players waiting for downloads
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Intro: QoE}
\begin{itemize}
	\item QoE means Quality of Experience
	\item Focuses on directing data flow to the user’s best interests first
	\begin{itemize}
		\item For example, downloading their character’s running animations, before downloading the distant city of Goradonia
	\end{itemize}
	\item Commonly used in video streaming to balance motion and detail
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{User experience != bitrate}
\begin{itemize}
\item User experience is more complex!
\item For example, evidence suggests users prefer a smooth low-quality video over higher-quality, inconsistent video \cite{qoesmallstudy} \cite{qoelargestudy}
\item The amount of action in a scene can affect their perception \cite{qoelargestudy}
\begin{itemize}
\item More action, less focus on detail. Less action, more focus. Could this apply to games as well?
\end{itemize}
\item In a nutshell, intelligent prioritising of streams is key
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Prerequisites: Map streaming}
\begin{itemize}
	\item To identify ideal architectures for implementing QoE map streaming, let’s explore the necessary ingredients
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Prerequisites - Baseline}
\begin{itemize}
\item Map data uploader
\begin{itemize}
	\item Sends map data to clients
\end{itemize}
\item Map data downloader
\begin{itemize}
	\item Takes map data from server
	\item Must tolerate incomplete data
\end{itemize}
\item Map constructor
\begin{itemize}
	\item Builds the map in real-time
	\item May include collision generation, textures, and LoD
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Prerequisites - With QoE}
\begin{itemize}
	\item Map data prioritiser
	\begin{itemize}
		\item Decides which map data each player needs soonest
		\item Must work with data uploader
	\end{itemize}
	\item Map data compressors
	\begin{itemize}
		\item Reduces bandwidth by brute force
		\item Adds processing time on downloads: may introduce FPS lag
	\end{itemize}
	\item `Network LOD' generators
	\begin{itemize}
		\item Reduces details on distant player-made areas
		\item Different to regular LOD--regular LOD is predefined on your local PC
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Preliminary architectural theories}
\begin{itemize}
\item Multi-threading
\begin{itemize}
	\item Could reduce distressing lag during downloads
\end{itemize}
\item Adapters?
\begin{itemize}
	\item Could wrap compressed map data into usable geometry
\end{itemize}
\item Observers?
\begin{itemize}
	\item Could live in the map class, awaiting incoming map data
\end{itemize}
\item Or mediators?
\begin{itemize}
	\item Alternative to data transferral between networked map data and geometry
	\item Which one is better?
\end{itemize}
\item OOP?
\begin{itemize}
	\item OOP principles support all the above design patterns quite well
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{More to come}
\begin{itemize}
	\item More specific design patterns will be isolated pending further research into existing game titles
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Any questions?}
\begin{itemize}
	\item References:
\end{itemize}
\bibliographystyle{ieeetr}
\bibliography{references_presentation}
\end{frame}

\end{document}